### 2017-12-30 Paper/examples.tex
borehole in progress

In Section~\ref{sec:method}, we presented a methodology for screening model
parameters using an approximate estimate of the upper bound on the Sobol'
total effect sensitivity index. The screening process helped identify parameters
that are relatively insignificant with respect to the observable. These insignificant
parameters could thus be fixed at their nominal values thereby reducing the
dimensionality of the problem.

@@

\be
\epsilon_{\mbox{\tiny LOO}} = 
\frac{\sum_{i=1}^N\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - 
 \mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\theta}_i)\right)^2}
{\sum_{i=1}^N
\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - \widetilde{\mu}\right)^2}
\label{eq:loo}
\ee

@@

@@

Our goal as discussed is to gain computational advantage by constructing surrogates in a 
reduced input parameter space. To this end, we construct PCE's in 5D and 4D spaces by
fixing $\{T_u,T_l\}$ in the former and additionally fixing $K_w$ in the latter at their respective
mean values. In Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed
in the full space (7D) with those constructed in the two reduced spaces (4D and 5D) using
$\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). As expected, it is observed that the PCE
constructed in the 4D space converges at a much faster rate. For instance, if a PCE with
$\mathcal{O}(10^{-6})$ accuracy is sought, we need

>>>>

In section~\ref{sec:method}, we presented a methodology for screening model
parameters using an approximate estimate of the upper bound on the Sobol'
total effect sensitivity index. The screening process helped identify parameters
that are relatively insignificant with respect to the observable. These insignificant
parameters could thus be fixed at their nominal values thereby reducing the
dimensionality of the problem.

@@

\be
\epsilon_{\mbox{\tiny LOO}} = 
\frac{\sum_{i=1}^N\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - 
 \mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\xi(\theta}_i))\right)^2}
{\sum_{i=1}^N
\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - \widetilde{\mu}\right)^2}
\label{eq:loo}
\ee

@@

The converged low-dimensional PCE is assessed
for predictive accuracy. While several techniques could be used, we consider predictive verification
in an L-2 sense as well as a probabilistic sense. In the former case, we estimate a relative L-2 norm
of the error ($\epsilon_{\mbox{\tiny{L-2}}}$) as follows:

\be
\epsilon_{\mbox{\tiny{L-2}}} = 
\frac{\left[\sum_{i=1}^N\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - 
 \mathcal{Y}^{\mbox{\tiny {PC}}}(\bm{\xi(\theta}_i))\right)^2\right]^{\frac{1}{2}}}
{\left[\sum_{i=1}^N
\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}}
\label{eq:l2}
\ee

\noindent As discussed earlier in section~\ref{sec:method}, computational cost associated with
L-2 verification is negligible since function evaluations or model realizations obtained during the
screening step could be re-used.
However, since the test problems are computationally inexpensive, we generate an independent
set of samples ($\bm{\theta_i}$) to estimate $\epsilon_{\mbox{\tiny{L-2}}}$ using Eq.~\ref{eq:l2}
in each case.
For the purpose of probabilistic verification, we compare the probability density function of
the observable obtained using PCE's in the full space and the reduced space in the following
test problems. In situations where model runs are computationally expensive, probabilistic verification might
not be feasible.

@@

Our goal as discussed is to gain computational advantage by constructing surrogates in a 
reduced input parameter space. To this end, we construct PCE's in 5D and 4D spaces by
fixing $\{T_u,T_l\}$ in the former and additionally fixing $K_w$ in the latter at their respective
mean values. In Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed
in the full space (7D) with those constructed in the two reduced spaces (4D and 5D) using
$\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). As expected, it is observed that the PCE
constructed in the 4D space converges at a much faster rate. For instance, if a PCE with
$\mathcal{O}(10^{-4})$ accuracy is sought, we need function evaluations at only about
50 sample points in the 4D parameter space whereas the number of samples needed in the full 
7D space seems much higher.
